What We Eval in the Shadows

### 2021-08-13 paper/main.tex
Fixes

The R language was intended to be extensible. The combination of lazy
evaluation, \k{substitute} and \k{eval} are some of the tools given to
developers to this end. To understand \emph{why} developers use \eval, we
manually inspected top 117 sites which contribute to 90\% of the calls in the
corpus. In this section we show 10 real-world examples form this batch. The
goal is to illustrate the variety of use cases that employ \eval in the R
ecosystem. The code snippets are simplified for clarity.

\paragraph{Extended Interfaces}
Sometimes it is convenient to allow users to extend the behavior of a library
function. \Eval allows clients to provide a simple text string that shall be
executed in the context of the function. The example here allows users to
provide formulas as strings, such as \k{"exp(-x^2/2)"}, the contract being that
the text can refer to some variable \k{x} that will be set up by the called
function. In this case one users could provide an anonymous function.

@@

The \k{glue} package contains a variant that leverages the non-standard scoping
as well allowing to resolve interpolation in alternative environments. For
example, the following snippet pipes the subsetted data frame into the
\k{glue_data} function that uses it to resolve the symbols in string
interpolation.

>>>>

The R language was intended to be extensible. The combination of lazy
evaluation, \k{substitute} and \k{eval} are some of the tools given to
developers to this end. To understand \emph{why} developers use \eval, we
manually inspected top 117 sites which contribute to 90\% of the calls in the
corpus. In this section we show 10 real-world examples from this batch. The
goal is to illustrate the variety of use cases that employ \eval in the R
ecosystem. The code snippets are simplified for clarity.

\paragraph{Extended Interfaces} Sometimes it is convenient to allow users to
extend the behavior of a library function. \Eval allows clients to provide a
simple text string that shall be executed in the context of the function. The
example here allows users to provide formulas as strings, such as
\k{"exp(-x^2/2)"}, the contract being that the text can refer to some variable
\k{x} that will be set up by the called function.\footnote{The function is used
to generates a sequence of random numbers using the adaptive rejection sampling
algorithm and the string formula is used to describe the target density.} In
this case users could provide an anonymous function.

@@

The \k{glue} package contains a variant that leverages the non-standard scoping
as well allowing to resolve interpolation in an alternative environment. For
example, the following snippet pipes the subsetted data frame into the
\k{glue_data} function that uses it to resolve the symbols in string
interpolation.
